\OurTool{}: Integrative Probing Analysis of Nucleic Acids Empowered by Multiple Accessibility Profiles

### 2020-07-02 IPANEMAP-2019.tex
Updates from Overleaf

%\paragraph{Results description}
A first observation is that \OurTool generally outperforms \Software{RSample}, averaging $80\%$ GM as opposed to $68\%$ for its competitor. \RevA{The superiority on \OurTool on this benchmark appears statistically significant according to a two-tailed paired $t$-test (P-value$=6\times10^{-3}$) with observed data.}
Out of the 24 considered RNAs, \OurTool outperforms its competitor for 16 out of the 24 RNAs, achieves similar performances for 2 of them, and is dominated for the remaining 6 cases. Whenever dominant, \OurTool achieves an average GM score of $82\%$, dominating by $32.8\%$ its competitor, while being dominated by $3.5\%$ over the remaining examples (including ties). 
%Difference<-c(IPANEMAP-Rsample)
%> sum(Difference[1:18])
%[1] 3.17
%> sum(Difference[19:24])
%[1] -0.382
Remarkably, \OurTool predicts secondary structures much more consistently than its competitor. 
It ensures GM that are greater than 50\% in all cases, and even exceeds 60\% over all except for the yeast tRNA, encoding the Aspartic acid and HIV1 5' pseudoknot domain. The standard deviation of GM for \OurTool is $12.4\%$, compared to the larger value of $21\%$ for \Software{RSample} predictions.

@@

This observed discrepancy is somewhat surprising, given that \OurTool and \Software{RSample} share the same sampling/clustering based modeling. However, the two methods differ substantially whenever a single conformation is detected, in which case \Software{RSample} switches to a simple MEA prediction, whereas \OurTool{} always proceeds with an iterative clustering. This allows \OurTool{} to consider a larger number of clusters, which we believe helps eliminating structural outliers, leading to the election of an improved final centroid structure.

>>>>

%\paragraph{Results description}
%A first observation is that \OurTool generally outperforms \Software{RSample}, averaging $80\%$ GM as opposed to $68\%$ for its competitor. \RevA{The superiority on \OurTool on this benchmark appears statistically significant according to a two-tailed paired $t$-test (P-value$=6\times10^{-3}$) with observed data.}
%Out of the 24 considered RNAs, \OurTool outperforms its competitor for 16 out of the 24 RNAs, achieves similar performances for 2 of them, and is dominated for the remaining 6 cases. Whenever dominant, \OurTool achieves an average GM score of $82\%$, dominating by $32.8\%$ its competitor, while being dominated by $3.5\%$ over the remaining examples (including ties). 
%Difference<-c(IPANEMAP-Rsample)
%> sum(Difference[1:18])
%[1] 3.17
%> sum(Difference[19:24])
%[1] -0.382
%Remarkably, \OurTool predicts secondary structures much more consistently than its competitor. 
%It ensures GM that are greater than 50\% in all cases, and even exceeds 60\% over all except for the yeast tRNA, encoding the Aspartic acid and HIV1 5' pseudoknot domain. The standard deviation of GM for \OurTool is $12.4\%$, compared to the larger value of $21\%$ for \Software{RSample} predictions.

@@

%This observed discrepancy is somewhat surprising, given that \OurTool and \Software{RSample} share the same sampling/clustering based modeling. However, the two methods differ substantially whenever a single conformation is detected, in which case \Software{RSample} switches to a simple MEA prediction, whereas \OurTool{} always proceeds with an iterative clustering. This allows \OurTool{} to consider a larger number of clusters, which we believe helps eliminating structural outliers, leading to the election of an improved final centroid structure.
